---
title: "LCARS-M2 analysis template"
author: "N.N."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: united
    toc_float: yes
    toc: yes
    number_sections: yes
    code_folding: show
---

# Requirements
* R
* libsodium (if the data needs to be decrypted)


# Setup

* Place the **data file "scientific_dataset.csv.enc"** obtained from the server download in the **folder** named **"data"**.
* Place **key files "study.key" and "server.pub.key"** in the **keys folder** (you got these files from the server admin).
* Note: The encryption ensures that the data can only be accessed by the study's admin and that the data have not been hampered with (mutual authentication).

**Important note:** Data files (e.g. .csv), results (e.g. html) and key files should not be uploaded to version control systems (e.g. GitHub), unless you are okay with them being stored on these systems! These file extensions are **excluded** from upload (i.e. .csv, .html and .key). you can **modify** this behavior by editing **.gitignore**.


## Install R packages

Define required R packages. Install required packages for R if not yet installed. Finally, load packages.

```{r message=FALSE, warning=TRUE}
# R packages
req_packages = c(
  "readr",
  "dplyr",
  "DT",
  "knitr",
  "plotly",
  "base64enc",
  "ggplot2",
  "sodium" # requires libsodium library when pkg needs compiling.
)

# Install, if not installed yet (from CRAN)
all_pkg = installed.packages()
for (i in req_packages){
  if(i %in% all_pkg[,"Package"] == FALSE){
    utils::install.packages(i)
  }
}

# Load pakages
for (i in req_packages) {
  base::require(i, character.only = TRUE)
}
```


## Additional functions

### Data decryption

```{r}
read_decrpyt_data = function(study_key_file,
                 server_pub_key_file,
                 encrypted_dataset_file,
                 output_file,
                 output_format, # "csv" or "rds"
                 save_decrypted_data,
                 max_size # max size in bytes (a value of 100.000.000 value corresponds to 100 MB, adjust if more is needed!)
                 ) {
  
  keys <- read_delim("keys/keys.txt", delim = ":", 
    escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE) %>% as.data.frame()
  
  study_key = keys[keys[,1]=="Private study key",2]
  study_key = base64decode(study_key)
  
  server_pub_key = keys[keys[,1]=="Public server key",2]
  server_pub_key = base64decode(server_pub_key)
  
  enc_data = readBin(encrypted_dataset_file, what = "raw", n = max_size)[-(1:24)]
  
  nonce = readBin(encrypted_dataset_file, what = "raw", n = 24)
  
  dec_data = sodium::auth_decrypt(bin = enc_data,
                                  key = study_key,
                                  pubkey = server_pub_key,
                                  nonce = nonce)
  
  scientific_dataset = read.csv(text = rawToChar(dec_data), sep = ";") 
  
  if (save_decrypted_data == TRUE){
    if (output_format == "rds"){
      saveRDS(scientific_dataset, output_file)
    } else if (output_format == "csv"){
      readr::write_csv(scientific_dataset, output_file)
    }
  }
  
  return(scientific_dataset)
  
}
```


# Prepare data
Please modify/extend the script as needed.

## Import data

Read and decrypt the data obtained from the server.
```{r message=FALSE}
# Import
all_data = read_decrpyt_data(study_key_file = "keys/study.key",
                                  server_pub_key_file = "keys/server.pub.key",
                                  encrypted_dataset_file = "data/scientific_dataset.csv.enc",
                                  output_file = "data/scientific_dataset.csv",
                                  output_format = "csv",
                                  save_decrypted_data=TRUE,
                                  max_size = 100000000)
```


# Results

## Study overview
```{r}
n_study_sites = all_data %>% dplyr::filter(!duplicated(study_site)) %>% base::nrow()
n_participants = all_data %>% dplyr::filter(!duplicated(participant_pk)) %>% base::nrow()
submissions_by_site = all_data %>%
  dplyr::filter(!base::duplicated(c(base::paste(submission_pk)))) %>%
  dplyr::select(study_site, visit_id) %>%
  base::table() %>% 
  base::as.data.frame.matrix() %>%
  dplyr::as_tibble(rownames = "site")
```

In total, **`r n_study_sites` study sites** submitted data for this study, and data of **`r n_participants` participants** were included (participants with **at least one submission**).

### Table: submissions by site
```{r}
submissions_by_site %>% knitr::kable()
```
**Table. Submissions by site.** Distribution of submissions per study site.


### Figure: participants per site
```{r fig.height=8, fig.width=10}
pt_per_site = all_data %>%
  dplyr::filter(!duplicated(participant_pk)) %>%
  select(study_site) %>% table() %>%
  dplyr::as_tibble()
fig <- plotly::plot_ly(pt_per_site, labels = ~study_site, values = ~n, type = 'pie')
fig
```
**Figure. Participants by site.** Number of participants per study site with at least one submission per participant.
